Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}

```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
install.packages('ggplot2')
library(ggplot2)
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}

```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(x=friend_count, data= pf)
```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
qplot(x = friend_count, data = pf, binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))

```

### Exploring with Bin Width
Notes:

***
qplot(x=friend_count, data= pf, xlim = c (0,1000))
qplot(x=friend_count, data= subset(pf, !is.na(gender)), binwidth=25)+
  scale_x_continuous(limits= c(0,1000))+
  facet_wrap(~gender)
### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
pf <- read.csv("C:/Users/reem1/Desktop/NanoDegree Data Analyst/EDA/lesson3/pseudo_facebook.tsv", sep="\t")
naqplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}

```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
Notes:

```{r Tenure}

```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
ggplot(aes(x = tenure/365), data = pf) +
  geom_histogram(binwidth = 0.25, color = 'black', fill = '#099DD9')

```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
table(pf$gender)
 
by(pf$friend_count, pf$gender, summary)



ggplot(aes(x = tenure / 365), data = pf) +
  geom_histogram(color = 'black', fill = '#F79420') +
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7)) +
  xlab('Number of years using Facebook') +
  ylab('Number of users in sample')```

***

### User Ages
Notes:

``
ggplot(aes(x = age), data = pf) +
  geom_histogram(color = 'black', fill = '#F79420') +
  scale_x_continuous(breaks = seq(10, 100, 10), limits = c(13, 120)) +
  xlab('Ages of the users on Facebook') +
  ylab('Number of users in sample')


```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:
p1<-qplot(x=friend_count, data=pf,bins=100, xlim= c(0, 1000))
p2<-qplot(x=log10(friend_count+1), data=pf)
p3<-qplot(x=sqrt(friend_count), data=pf)
grid.arrange(p1, p2, p3,ncol=1)
### Add a Scaling Layerp
Notes:

```{r Add a Scaling Layer}

```

***


### Frequency Polygons

```{r Frequency Polygons}

```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
qplot(x=www_likes, data = subset(pf, !is.na(gender)), geom='freqpoly')+
  scale_x_continuous()+
  scale_x_log10()


```
by(pf$friendships_initiated, pf$gender, summary)


***

### Box Plots
Notes:

```{r Box Plots}

qplot(geom='boxplot', x= gender, y=friend_count, data= subset(pf, !is.na(gender)), ylim=c(0,1000))


qplot(geom='boxplot', x= gender, y=friendships_initiated, data= subset(pf, !is.na(gender)))+
  coord_cartesian(ylim=c(0,1000))
```
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}

```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}

```

Response:

***
r
### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!